---
title: "RACiR Curve Protocol for LI-6800, Bluestem version 1.4.0"
date: 'Last updated: 2020-07-29'
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Pre-start checklist

1. Check chemicals

* H$_2$O scrub: is dessicant fresh?
* H$_2$O add: is Stuttgarter Masse wet?
* CO$_2$ scrub: is soda lime fresh?

2. Connect CO$_2$

3. Connect sensor head

## Start-up

1. Turn on LI-6800

2. Load Factory settings

3. In "Start up" menu, go to "Warmup/System Tests". Run "Warmup Tests" (~15 minutes)

## Environment control

**Note:** These are "standard" environmental conditions and may change for a given experiment.

Go to "Environment" tab

 Parameter     | Reference     | Value
---------------|---------------|--------------------
 Flow          |               | $\mu$mol $s^{-1}$
 H$_2$O        | `VPD_leaf`    | 1.5 kPa
 CO$_2$        | `CO2_r`       | 410 ppm
 Fan           | `Speed`       | 10000 rpm
 Temperature   | `Tleaf`       | 25 $^\circ C$
 Light         | Setpoint      | 1000 $\mu$mol $m^{-2}$ $s^{-1}$ 
 Fluor         | Keep defaults | NA
 Auxilliary    | Keep defaults | NA
 Auto Controls | Target        | `CO2_r`
               | $F(t)$        | `Linear`
               | $F(0)$        | 10 ppm
               | $F(T)$        | 1010 ppm
               | Period        | 10 minutes

* Uncheck "Auto-Repeat"
* Make sure arrow is at beginning of ramp

## Acclimation

1. Once environmental parameters are set and have reached equilibrium, clamp onto a leaf to acclimate.

2. Once semi-stable, Match

3. Allow leaf to acclimate to chamber conditions until $A$ and $g_\text{sw}$ reach equilibrium (typically 10-30 minutes).

4. After leaf is fully acclimatized, Match again immediately before starting RACiR curve.

## Log files

You can do these steps while leaf is acclimating.
1. Navigate to Log Files tab

2. Under "Matching Options", set to "Never Match"

3. Under "Fluorometer Options", set to "Flr Action at Log" to "0: Nothing"

4. Under "Open a Log File", select "New File" and name "yyyy-mm-dd-fml-racir"

5. Under "Log Remark", indicate what you're measuring

```{r cars}
summary(cars)
```

## Start Auto Program

Navigate to "Auto Programs" tab